# Clean HBV model input data sets
# ===============================

Authors: Richard T. Gray, Neil Bretana

This script is used to load the data sets used in the original Berkely 
Madonna HBV model and save them in a tidy data frame format for use as 
input parameters. We do not read in the cumulative notifications file as 
this can be obtained from notifications. 

This script only needs to be run once to convert data files into the
format required for the model. 

```{r Initialization}
# Clear workspace
rm(list = ls()) 

# Setup directories after setting working directory to source file 
# directory (so it is easy to move code around)
basePath <- getwd()
dataPath <- file.path(basePath, "data") # original data stored in ./BM datasets
Rcode <- file.path(basePath, "code")

# Load useful libraries
source(file.path(Rcode, "LoadLibrary.R"))
LoadLibrary("readr")
LoadLibrary("dplyr")
LoadLibrary("tidyr")

# Output file names
paramFile1 <- "parameters_constant.csv"
paramFile2 <- "parameters_time_varying.csv"

```

```{r Data set details}
# This chuck specifies the files and associated variable names of the data 
# sets. Set up so the variable name and file can be easily extracted or 
# changed. 

constantsFile <- "Constants.csv"

completeDataFiles <- c("bgmort0to4" = "bgmort 0to4.csv",
               "bgmort5to14" = "bgmort 5to14.csv",
               "bgmort15to44"= "bgmort 15to44.csv", 
               "bgmort45" = "bgmort 45plus.csv",
               "births" = "births.csv", 
               "mig0to4chronic" = "mig 0to4 chronic.csv", 
               "mig0to4cleared" = "mig 0to4 cleared.csv", 
               "mig0to4sus" = "mig 0to4 sus.csv", 
               "mig5to14chronic" = "mig 5to14 chronic.csv", 
               "mig5to14cleared" = "mig 5to14 cleared.csv", 
               "mig5to14sus" = "mig 5to14 sus.csv", 
               "mig15to44chronic" = "mig 15to44 chronic.csv", 
               "mig15to44cleared" = "mig 15to44 cleared.csv", 
               "mig15to44sus" = "mig 15to44 sus.csv", 
               "mig45chronic" = "mig 45plus chronic.csv", 
               "mig45cleared" = "mig 45plus cleared.csv", 
               "mig45sus" = "mig 45plus sus.csv")

notificationsFile<- c("notifications2014.csv")

```

# Constants

```{r load and save constants}
constants <- read_csv(file.path(dataPath, "BM datasets", constantsFile))
constants <-  gather(constants, "parameter", "value", 1:ncol(constants))

write.csv(constants, file.path(dataPath, paramFile1), row.names=FALSE)

```

# Time varying parameters

Note the time varying parameters are stored as simple CSV files. They 
sometimes contain additional data or other relevant information. We have 
only the second column. 

```{r Load and save time varying data}
# This chunk reads in all the BM data files and merges the columns into a 
# single data frame

numYears <- 100 # 1951:2050
numCols <- length(completeDataFiles) + 1 # include year column

bmData <- data.frame(matrix(ncol = numCols, nrow = numYears))

# Load the complete data set files and append to our final data frame
for (file in 1:length(completeDataFiles)) {
  tempData <- read_csv(file.path(dataPath, "BM datasets", 
                                 completeDataFiles[file]),
                       col_names = FALSE)
  
  bmData[, file + 1] <- tempData[1:numYears, 2]
  colnames(bmData)[file + 1] <- names(completeDataFiles)[file]
}

# Add years to first column
bmData[, 1] <- tempData[1:numYears, 1]
colnames(bmData)[1] <- "year"

# Now append notifications
diags <- read_csv(file.path(dataPath, "BM datasets", notificationsFile),
         col_names = c("year", "notifications"))

bmData <- left_join(bmData, diags, by = "year")

# Write final data frame to file
write_csv(bmData, file.path(dataPath, paramFile2))

```
