---
title: "Australia HBV Model Summary Results"
author: "Richard T. Gray"
date: Latest version - `r format(Sys.Date(), format="%B %d %Y")`
output: 
  word_document:
    pandoc_args: --output="docs/Summary_results.docx"
    reference_docx: docs/mystyles.docx
---

<!---This Rmarkdown scipt generates the summary figures and outputs from
the results generated using the ECDC HIV Modelling Tool. --->

```{r knitr_options, include=FALSE} 
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE, 
                      include = FALSE) 
```

This document presents the summary results for the baseline scenario in
the Australian HBV model. 

```{r Initialize script}
# Clear workspace and plots
rm(list = ls()) 
graphics.off()

# Setup directories after setting working directory to source file 
# directory (so it is easy to move code around)
basePath <- getwd()
Rcode <- file.path(basePath, "code")
projectFolder <- file.path(basePath, "projects")

# Load useful libraries
source(file.path(Rcode, "LoadLibrary.R"))
source(file.path(Rcode, "DataLibraries.R"))
source(file.path(Rcode, "PlotOptions.R"))
LoadLibrary(cowplot)

# Wrapper function so we don't have to keep entering everything in
# ggsave. Plot defaults are put in the figure defaults
SaveFigure <- function(folder, filename, figure, 
                       format = ".png", height = 10, 
                       units = "cm", ...) {
  save_plot(file.path(folder, paste0(filename, format)), 
         figure, 
         base_height = height, units = units, ...)
}

```

```{r User sepcifications}
# Specify project to run
project <- "Australia_HBV_estimates-BM"

# Plotting options
displayPlots <- TRUE
savePlots <- TRUE

```

```{r Load project results}
# This loads all the project parameters and results including 
# bestResults

projectFile <- file.path(projectFolder, project, paste0(project, ".rda"))
load(projectFile)
```

```{r Generate plots}

# Population sizes ------------------------------------------------------

# First convert results population sizes into a massize data frame -------
popSizes <- as.data.frame.table(bestResults$allPops)
colnames(popSizes) <- c("age_group", "state", "time_step", "popsize") 
popSizes$time_step <- as.numeric(popSizes$time_step)

popSizes <- popSizes %>% # add pts as well
  mutate(year = pg$start_year + (time_step-1) * pg$timestep) 

# Total population size 
# Alternative using apply
# popSizes <- apply(bestResults$allPops, 3, function(x) rowSums(x))


# totalPop <- data_frame(time = pg$pts,
#            population = colSums(popSizes))

totalPop <- popSizes %>%
  group_by(year) %>%
  summarise(totalpop = sum(popsize)) 

totalPopPlot <- ggplot(data = totalPop, aes(x = year, y = totalpop)) +
  geom_line(colour = "blue") +
  xlab("Year") + ylab("Population size") +
  scale_x_continuous(breaks = seq(pg$start_year, pg$end_year +1, 
                                  by = 20)) +
  plotOpts

# Population size per age
# popSizesAge <- as.data.frame(t(popSizes))
# popSizesAge$time <- pg$pts
# 
# popSizesAge <- popSizesAge %>%
#   select(time, everything()) %>%
#   gather("age_group", "population", 2:(pg$npops+1))

popSizesAge <- popSizes %>%
  group_by(year, age_group) %>%
  summarise(totalpop = sum(popsize)) %>%
  ungroup() %>%
  arrange(age_group)

# Plot of population size in every group
plotAgePops <- popSizesAge
plotAgePops$age_group <- factor(plotAgePops$age_group)
levels(plotAgePops$age_group) <- c("Age < 4", "Age 5 to 14", 
                                   "Age 15 to 44", "Age > 45") # rename levels for plotting

agePopPlot <- ggplot(data = plotAgePops, 
                     aes(x = year, y = totalpop, group = age_group)) +
  geom_line(colour = "blue") +
  facet_wrap(~age_group, ncol = 2, scales = "free_x") + 
  scale_x_continuous(breaks = seq(pg$start_year, pg$end_year +1, 
                                  by = 50)) +
  xlab("Year") + ylab("Population size") +
  plotOpts + theme(panel.margin = unit(2, "lines"))

# Population prevalence --------------------------------------------------

# Data frame for overall number of people infected by age 
# Haven't produced a plot of this
infectSizes <-  popSizes %>%
  group_by(year, age_group) %>%
  filter(state != "s") %>% # exclude susceptibles
  summarise(totalpop = sum(popsize)) 

# Plot of population size in every group
plotPops <- popSizes
plotPops$age_group <- factor(plotPops$age_group)
levels(plotPops$age_group) <- c("Age < 4", "Age 5 to 14", "Age 15 to 44",
                                "Age > 45") # rename levels for plotting

allPopsPlot <- ggplot(data = plotPops, 
                      aes(x = year, y = popsize, group = state)) +
  facet_wrap(~age_group, ncol = 2, scales = "free_x") +
  geom_line(aes(colour = state)) +
  scale_x_continuous(breaks = seq(pg$start_year, pg$end_year +1, 
                                  by = 50)) +
  scale_colour_brewer(name = "Infection state", palette = "Set1",
                      labels = c("Susceptible", "Acute", "Chronic",
                                 "Cleared", "Immune")) +
  xlab("Year") + ylab("Population size") +
  plotOpts + theme(legend.position = "right") + 
  theme(panel.margin = unit(2, "lines"))

# Neil's code ------------------------------------------------------------

# allPops population per ge group
# allPops0s <- NULL
# allPops0s$n <- c(bestResults$allPops[1,"s",])
# allPops0s$npts <- c(1:length(bestResults$allPops[1,"s",]))
# allPops0s$state <- "susceptible"
# allPops0s$pops <- "age0to4"
# allPops0a <- NULL
# allPops0a$n <- c(bestResults$allPops[1,"a",])
# allPops0a$npts <- c(1:length(bestResults$allPops[1,"a",]))
# allPops0a$state <- "acute"
# allPops0a$pops <- "age0to4"
# allPops0ch <- NULL
# allPops0ch$n <- c(bestResults$allPops[1,"ch",])
# allPops0ch$npts <- c(1:length(bestResults$allPops[1,"ch",]))
# allPops0ch$state <- "chronic"
# allPops0ch$pops <- "age0to4"
# allPops0cl <- NULL
# allPops0cl$n <- c(bestResults$allPops[1,"cl",])
# allPops0cl$npts <- c(1:length(bestResults$allPops[1,"cl",]))
# allPops0cl$state <- "cleared"  
# allPops0cl$pops <- "age0to4"
# allPops0i <- NULL
# allPops0i$n <- c(bestResults$allPops[1,"i",])
# allPops0i$npts <- c(1:length(bestResults$allPops[1,"i",]))
# allPops0i$state <- "immune"
# allPops0i$pops <- "age0to4"
# 
# #  allPops0 <- NULL
# #  allPops0 <- rbind(as.data.frame(allPops0s), as.data.frame(allPops0a), as.data.frame(allPops0ch), as.data.frame(allPops0cl), as.data.frame(allPops0i))
# #  ggplot(data=allPops0, aes(x= npts, y= n, group=state)) + geom_line(aes(color=state)) + xlab("year") + ylab("number of people") + ggtitle("Population") 
# 
# allPops1s <- NULL
# allPops1s$n <- c(bestResults$allPops[2,"s",])
# allPops1s$npts <- c(1:length(bestResults$allPops[2,"s",]))
# allPops1s$state <- "susceptible"
# allPops1s$pops <- "age5to14"
# allPops1a <- NULL
# allPops1a$n <- c(bestResults$allPops[2,"a",])
# allPops1a$npts <- c(1:length(bestResults$allPops[2,"a",]))
# allPops1a$state <- "acute"
# allPops1a$pops <- "age5to14"
# allPops1ch <- NULL
# allPops1ch$n <- c(bestResults$allPops[2,"ch",])
# allPops1ch$npts <- c(1:length(bestResults$allPops[2,"ch",]))
# allPops1ch$state <- "chronic"
# allPops1ch$pops <- "age5to14"
# allPops1cl <- NULL
# allPops1cl$n <- c(bestResults$allPops[2,"cl",])
# allPops1cl$npts <- c(1:length(bestResults$allPops[2,"cl",]))
# allPops1cl$state <- "cleared"
# allPops1cl$pops <- "age5to14"
# allPops1i <- NULL
# allPops1i$n <- c(bestResults$allPops[2,"i",])
# allPops1i$npts <- c(1:length(bestResults$allPops[2,"i",]))
# allPops1i$state <- "immune"
# allPops1i$pops <- "age5to14"
# 
# allPops2s <- NULL
# allPops2s$n <- c(bestResults$allPops[3,"s",])
# allPops2s$npts <- c(1:length(bestResults$allPops[3,"s",]))
# allPops2s$state <- "susceptible"
# allPops2s$pops <- "age15to44"
# allPops2a <- NULL
# allPops2a$n <- c(bestResults$allPops[3,"a",])
# allPops2a$npts <- c(1:length(bestResults$allPops[3,"a",]))
# allPops2a$state <- "acute"  
# allPops2a$pops <- "age15to44"
# allPops2ch <- NULL
# allPops2ch$n <- c(bestResults$allPops[3,"ch",])
# allPops2ch$npts <- c(1:length(bestResults$allPops[3,"ch",]))
# allPops2ch$state <- "chronic"  
# allPops2ch$pops <- "age15to44"
# allPops2cl <- NULL
# allPops2cl$n <- c(bestResults$allPops[3,"cl",])
# allPops2cl$npts <- c(1:length(bestResults$allPops[3,"cl",]))
# allPops2cl$state <- "cleared"  
# allPops2cl$pops <- "age15to44"
# allPops2i <- NULL
# allPops2i$n <- c(bestResults$allPops[3,"i",])
# allPops2i$npts <- c(1:length(bestResults$allPops[3,"i",]))
# allPops2i$state <- "immune"  
# allPops2i$pops <- "age15to44"
# 
# allPops3s <- NULL
# allPops3s$n <- c(bestResults$allPops[4,"s",])
# allPops3s$npts <- c(1:length(bestResults$allPops[4,"s",]))
# allPops3s$state <- "susceptible"  
# allPops3s$pops <- "age45"
# allPops3a <- NULL
# allPops3a$n <- c(bestResults$allPops[4,"a",])
# allPops3a$npts <- c(1:length(bestResults$allPops[4,"a",]))
# allPops3a$state <- "acute"  
# allPops3a$pops <- "age45"
# allPops3ch <- NULL
# allPops3ch$n <- c(bestResults$allPops[4,"ch",])
# allPops3ch$npts <- c(1:length(bestResults$allPops[4,"ch",]))
# allPops3ch$state <- "chronic"  
# allPops3ch$pops <- "age45"
# allPops3cl <- NULL
# allPops3cl$n <- c(bestResults$allPops[4,"cl",])
# allPops3cl$npts <- c(1:length(bestResults$allPops[4,"cl",]))
# allPops3cl$state <- "cleared"  
# allPops3cl$pops <- "age45"
# allPops3i <- NULL
# allPops3i$n <- c(bestResults$allPops[4,"i",])
# allPops3i$npts <- c(1:length(bestResults$allPops[4,"i",]))
# allPops3i$state <- "immune"  
# allPops3i$pops <- "age45"
# 
# allPops <- NULL
# allPops <- rbind(as.data.frame(allPops0s), as.data.frame(allPops0a), as.data.frame(allPops0ch), as.data.frame(allPops0cl), as.data.frame(allPops0i), as.data.frame(allPops1s), as.data.frame(allPops1a), as.data.frame(allPops1ch), as.data.frame(allPops1cl), as.data.frame(allPops1i), as.data.frame(allPops2s), as.data.frame(allPops2a), as.data.frame(allPops2ch), as.data.frame(allPops2cl), as.data.frame(allPops2i), as.data.frame(allPops3s), as.data.frame(allPops3a), as.data.frame(allPops3ch), as.data.frame(allPops3cl), as.data.frame(allPops3i))
# allPops <- ggplot(data=allPops, aes(x= npts, y= n, group=state)) + geom_line(aes(color=state)) + xlab("year") + ylab("number of people") + ggtitle("Population by age group") 
# allPops + facet_wrap( ~ pops, ncol=2)
# 
# #total population --------------------------------------------------------
# totalPops <- NULL
# totalPops$n <- as.data.frame(allPops0s$n) + as.data.frame(allPops0a$n) + as.data.frame(allPops0ch$n) + as.data.frame(allPops0cl$n) + as.data.frame(allPops0i$n) + as.data.frame(allPops1s$n) + as.data.frame(allPops1a$n) + as.data.frame(allPops1ch$n) + as.data.frame(allPops1cl$n) + as.data.frame(allPops1i$n) + as.data.frame(allPops2s$n) + as.data.frame(allPops2a$n) + as.data.frame(allPops2ch$n) + as.data.frame(allPops2cl$n) + as.data.frame(allPops2i$n) + as.data.frame(allPops3s$n) + as.data.frame(allPops3a$n) + as.data.frame(allPops3ch$n) + as.data.frame(allPops3cl$n) + as.data.frame(allPops3i$n)
# totalPops$npts <- c(1:length(allPops0s$n))
# totalPops <- as.data.frame(totalPops)
# colnames(totalPops) <- c("n", "npts")
# ggplot(data=totalPops, aes(x= npts, y= n)) + geom_line() + xlab("year") + ylab("number of people") + ggtitle("Total Population") 


#newInfections over time
# newInfections0 <- NULL
# newInfections0$n <- c(bestResults$newInfections[1,])
# newInfections0$npts <- c(1:length(bestResults$newInfections[1,]))
# newInfections0$pops <- "age0to4"
# newInfections1 <- NULL
# newInfections1$n <- c(bestResults$newInfections[2,])
# newInfections1$npts <- c(1:length(bestResults$newInfections[2,]))
# newInfections1$pops <- "age5to14"
# newInfections2 <- NULL
# newInfections2$n <- c(bestResults$newInfections[3,])  
# newInfections2$npts <- c(1:length(bestResults$newInfections[3,]))
# newInfections2$pops <- "age15to44"
# newInfections3 <- NULL
# newInfections3$n <- c(bestResults$newInfections[4,])    
# newInfections3$npts <- c(1:length(bestResults$newInfections[4,]))
# newInfections3$pops <- "age45"
# 
# newInfections <- NULL
# newInfections <- rbind(as.data.frame(newInfections0), as.data.frame(newInfections1), as.data.frame(newInfections2), as.data.frame(newInfections3))

newInfections <- as.data.frame(t(bestResults$newInfections)) %>%
  mutate(year = pg$pts) %>%
  select(year, everything()) %>%
  gather("age_group", "infections", 2:(pg$npops+1)) %>%
  mutate(incidence = infections / popSizesAge$totalpop)

newInfectionsPlot <- ggplot(data = newInfections, 
    aes(x = year, y = infections, group= age_group)) +
  geom_line(aes(color = age_group)) + 
  xlab("Year") + ylab("New infections") +
  scale_x_continuous(breaks = seq(pg$start_year, pg$end_year +1, 
                                  by = 20)) +
  scale_colour_brewer(name = "Age Group", palette = "Set1",
                      labels = c("Age < 4", "Age 5 to 14", "Age 15 to 44",
                                "Age > 45")) + 
  plotOpts + theme(legend.position = "right")

# newInfectionsPlot

#incidence over time (newInfections / totalPops per time) ----------------
# incidence0 <- NULL
# incidence0$n <- c(bestResults$newInfections[1,]/totalPops$n)
# incidence0$npts <- c(1:length(bestResults$newInfections[1,]))
# incidence0$pops <- "age0to4"
# incidence1 <- NULL
# incidence1$n <- c(bestResults$newInfections[2,]/totalPops$n)
# incidence1$npts <- c(1:length(bestResults$newInfections[2,]))
# incidence1$pops <- "age5to14"
# incidence2 <- NULL
# incidence2$n <- c(bestResults$newInfections[3,]/totalPops$n)  
# incidence2$npts <- c(1:length(bestResults$newInfections[3,]))
# incidence2$pops <- "age15to44"
# incidence3 <- NULL
# incidence3$n <- c(bestResults$newInfections[4,]/totalPops$n)    
# incidence3$npts <- c(1:length(bestResults$newInfections[4,]))
# incidence3$pops <- "age45"
# 
# incidence <- NULL
# incidence <- rbind(as.data.frame(incidence0), as.data.frame(incidence1), as.data.frame(incidence2), as.data.frame(incidence3))

incidencePlot <- ggplot(data = newInfections, 
  aes(x = year, y = incidence * 1e5, group = age_group)) + 
  geom_line(aes(color = age_group)) + 
  xlab("year") + ylab("Incidence per 100,000") +
  scale_x_continuous(breaks = seq(pg$start_year, pg$end_year +1, 
                                  by = 20)) +
  scale_colour_brewer(name = "Age Group", palette = "Set1",
                      labels = c("Age < 4", "Age 5 to 14", "Age 15 to 44",
                                "Age > 45")) +
  plotOpts + theme(legend.position = "right")
  
# incidencePlot

#####

#prevalence per age group
# prevalentCases0 <- NULL
# prevalentCases0$n <- c(0 + cumsum(newInfections0$n))
# prevalentCases0$npts <- c(1:length(newInfections0$n))
# prevalentCases0$pops <- "age0to4"
# prevalentCases1 <- NULL
# prevalentCases1$n <- c(0 + cumsum(newInfections1$n))
# prevalentCases1$npts <- c(1:length(newInfections0$n))
# prevalentCases1$pops <- "age5to14"
# prevalentCases2 <- NULL
# prevalentCases2$n <- c(0 + cumsum(newInfections2$n))  
# prevalentCases2$npts <- c(1:length(newInfections0$n))
# prevalentCases2$pops <- "age15to44"
# prevalentCases3 <- NULL
# prevalentCases3$n <- c(0 + cumsum(newInfections3$n))    
# prevalentCases3$npts <- c(1:length(newInfections0$n))
# prevalentCases3$pops <- "age45"
# 
# prevalentCases <- NULL
# prevalentCases <- rbind(as.data.frame(prevalentCases0), as.data.frame(prevalentCases1), as.data.frame(prevalentCases2), as.data.frame(prevalentCases3))
# prevalentCasesPlot <- ggplot(data=prevalentCases, aes(x= npts, y= n, group=pops)) + geom_line(aes(color=pops)) + xlab("year") + ylab("number of people") + ggtitle("Prevalent HBV infections") 
# # prevalentCasesPlot

#total prevalence over time
# prevalence0 <- NULL
# prevalence0$n <- c(prevalentCases0$n/totalPops$n)
# prevalence0$npts <- c(1:length(prevalentCases0$n))
# prevalence0$pops <- "age0to4"
# prevalence1 <- NULL
# prevalence1$n <- c(prevalentCases0$n/totalPops$n)
# prevalence1$npts <- c(1:length(prevalentCases0$n))
# prevalence1$pops <- "age5to14"
# prevalence2 <- NULL
# prevalence2$n <- c(prevalentCases0$n/totalPops$n)  
# prevalence2$npts <- c(1:length(prevalentCases0$n))
# prevalence2$pops <- "age15to44"
# prevalence3 <- NULL
# prevalence3$n <- c(prevalentCases0$n/totalPops$n)    
# prevalence3$npts <- c(1:length(prevalentCases0$n))
# prevalence3$pops <- "age45"
# 
# prevalence <- NULL
# prevalence <- rbind(as.data.frame(prevalence0), as.data.frame(prevalence1), as.data.frame(prevalence2), as.data.frame(prevalence3))
# prevalencePlot <- ggplot(data=incidence, aes(x= npts, y= n, group=pops)) + geom_line(aes(color=pops)) + xlab("year") + ylab("number of people") + ggtitle("HBV prevalence") 
# # prevalencePlot
# 
# #HBV treatment 
# HBVtreatments0 <- NULL
# HBVtreatments0$n <- c(bestResults$newTreatments[1,])
# HBVtreatments0$npts <- c(1:length(bestResults$newTreatments[1,]))
# HBVtreatments0$pops <- "age0to4"
# HBVtreatments1 <- NULL
# HBVtreatments1$n <- c(bestResults$newTreatments[2,])
# HBVtreatments1$npts <- c(1:length(bestResults$newTreatments[2,]))
# HBVtreatments1$pops <- "age5to14"
# HBVtreatments2 <- NULL
# HBVtreatments2$n <- c(bestResults$newTreatments[3,])  
# HBVtreatments2$npts <- c(1:length(bestResults$newTreatments[3,]))
# HBVtreatments2$pops <- "age15to44"
# HBVtreatments3 <- NULL
# HBVtreatments3$n <- c(bestResults$newTreatments[4,])    
# HBVtreatments3$npts <- c(1:length(bestResults$newTreatments[4,]))
# HBVtreatments3$pops <- "age45"
# 
# HBVtreatments <- NULL
# HBVtreatments <- rbind(as.data.frame(HBVtreatments0), as.data.frame(HBVtreatments1), as.data.frame(HBVtreatments2), as.data.frame(HBVtreatments3))
# HBVtreatmentsPlot <- ggplot(data=HBVtreatments, aes(x= npts, y= n, group=pops)) + geom_line(aes(color=pops)) + xlab("year") + ylab("number of people") + ggtitle("Treated HBV cases") 
# # HBVtreatmentsPlot
# 
# #HBV deaths
# HBVdeaths0 <- NULL
# HBVdeaths0$n <- c(bestResults$newHBVdeaths[1,])
# HBVdeaths0$npts <- c(1:length(bestResults$newHBVdeaths[1,]))
# HBVdeaths0$pops <- "age0to4"
# HBVdeaths1 <- NULL
# HBVdeaths1$n <- c(bestResults$newHBVdeaths[2,])
# HBVdeaths1$npts <- c(1:length(bestResults$newHBVdeaths[2,]))
# HBVdeaths1$pops <- "age5to14"
# HBVdeaths2 <- NULL
# HBVdeaths2$n <- c(bestResults$newHBVdeaths[3,])  
# HBVdeaths2$npts <- c(1:length(bestResults$newHBVdeaths[3,]))
# HBVdeaths2$pops <- "age15to44"
# HBVdeaths3 <- NULL
# HBVdeaths3$n <- c(bestResults$newHBVdeaths[4,])    
# HBVdeaths3$npts <- c(1:length(bestResults$newHBVdeaths[4,]))
# HBVdeaths3$pops <- "age45"
# 
# HBVdeaths <- NULL
# HBVdeaths <- rbind(as.data.frame(HBVdeaths0), as.data.frame(HBVdeaths1), as.data.frame(HBVdeaths2), as.data.frame(HBVdeaths3))
# HBVdeathsPlot <- ggplot(data=HBVdeaths, aes(x= npts, y= n, group=pops)) + geom_line(aes(color=pops)) + xlab("year") + ylab("number of people") + ggtitle("HBV deaths") 
# HBVdeathsPlot

# Display plots (if required) --------------------------------------------

if (displayPlots) {
  totalPopPlot
  agePopPlot
  newInfectionsPlot
  incidencePlot
  allPopsPlot
}

# Save plots separately (if required) ------------------------------------
if (savePlots) {
  
  figureFolder <- file.path(projectFolder, project, "results")
  
  SaveFigure(figureFolder, "total_population", totalPopPlot)
  SaveFigure(figureFolder, "age_group_population", agePopPlot)
  SaveFigure(figureFolder, "new_infections", newInfectionsPlot)
  SaveFigure(figureFolder, "incidence", incidencePlot)
  SaveFigure(figureFolder, "all_pops_states", allPopsPlot)
}
```

## Summary Figures

### Total population size

**Figure 1** - Total population size over time.

```{r Insert figure 1, include = TRUE}
totalPopPlot
```

**Figure 2** - Population size by age group over time.

```{r Insert figure 2, include = TRUE}
agePopPlot
```


### New infections and incidence

**Figure 3** - New infections by age group.

```{r Insert figure 3, include = TRUE}
newInfectionsPlot
```

**Figure 4** - Incidence per 100,000 people by age group.

```{r Insert figure 4, include = TRUE}
incidencePlot
```

### Prevalence

**Figure 5** - Number of people in each stage of infection by age_group.

```{r Insert figure 5, include = TRUE}
allPopsPlot
```


